---
title:  "Econ 4743, Problem Set 3"
# author: "Abel Embaye"
# institute: |
#         | Department of Economics
#         |
#         | UofA
#         |
# date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pagedown::html_paged:
    number_sections: FALSE
    css:
     - ../../../../../_Fns/mypagesetting.css
    #toc: true
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: true
newpage_html_class: page-break
# lot: true # insert a list of tables
# lof: true # insert a list of figures
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print #prints pdf file in addition to paged html file
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = F)
options(kableExtra.latex.load_packages = FALSE)
pkgs<- c("knitr","quantmod", "ggplot2", "Quandl", "xts", "lubridate", "tikzDevice", "graphics", "gridExtra", "tidyverse",
         "plotrix", "png", "pdftools", "xtable", "readxl", "grid",  "dplyr", "ggrepel", "reshape2", "kableExtra", "magick", "formattable", "PoEdata", "wooldridge" ); pkgs
for (i in 1:length(pkgs)) {library(pkgs[i], character.only=T)} 
options(warinings=-1)
options(scipen=999)
```

```{r, echo=F}
#knitr::knit_exit() 
```

<h1>{{ student_name }}</h1>

question 1.1) short answer

<div style="width:200px; height:60px; padding:20px; text-align:center; border: 1px solid #787878">

{{ `r paste0("q", gg)` }}

</div> 

<br><br>

`r gg<- gg+1 `

`r gg`. and how much of the tax will be born by sellers ? (enter numeric input)

<div style="width:200px; height:60px; padding:20px; text-align:center; border: 1px solid #787878">

{{ `r paste0("q", gg)` }}

</div> 

<br><br>

`r gg=gg+1 `

`r gg`. Show the previous question graphically and Upload a snippet of your graph as image (.PNG, .JPG, .JEPG, .PDF, no HEIC please)

<div style="width:700px; height:550px; padding:20px; text-align:center; border: 1px solid #787878">

<img src="data:image/png;base64,{{ `r paste0("q", gg)` }}" />

</div>



# II. Deadweight loss (Chapter 20):

Suppose that in the country of Tributia a worker’s supply of labor is given by $H = 140W$, and a firm’s demand for labor by $H= 2000 – 20W$, where $W$ is wage per hour, and $H$ is quantity of hours worked.

Suppose that the government of Tributia decides to impose a proportional income tax of 25\% on all of the worker's earnings. 

`r gg<- gg+1 `

`r gg`. How much dead-weight-loss will be incurred? (enter numeric input)

<div style="width:200px; height:60px; padding:20px; text-align:center; border: 1px solid #787878">

{{ `r paste0("q", gg)` }}

</div> 

<br><br>

`r gg=gg+1 `

`r gg`. Show our calculations in a piece of paper clearly and Upload a snippet of that as image (.PNG, .JPG, .JEPG, .PDF, no HEIC please)

<div style="width:700px; height:550px; padding:20px; text-align:center; border: 1px solid #787878">

<img src="data:image/png;base64,{{ `r paste0("q", gg)` }}" />

</div>

<br><br>

`r gg=gg+1 `

`r gg`. Show graphically that a progressive tax is less efficient than flat tax by drawing two supply demand diagrams for low and high wage earners as discussed in class or the book. Upload a snippet of your graph and explanation as as image (.PNG, .JPG, .JEPG, .PDF, no HEIC please)

<div style="width:700px; height:550px; padding:20px; text-align:center; border: 1px solid #787878">

<img src="data:image/png;base64,{{ `r paste0("q", gg)` }}" />

</div>
 

```{r echo=F}
knitr::knit_exit()
```
